Design and Implementation of Probabilistic Programming Language Anglican

### 2016-08-03 paper/paper.tex
minor

@@

\section{Introduction}
For data science practitioners, statistical inference is typically
but one step in a more elaborate analysis workflow. The first stage
of this work involves data acquisition, pre-processing and cleaning.
This is often followed by several iterations of exploratory model
design and testing of inference algorithms. Once a sufficiently
robust statistical model and corresponding inference algorithm have
been identified, analysis results must be post-processed, visualized,
and in some cases integrated into a wider production system.

@@

>>>>

\newcommand*{\dt}[1]{{ \bf [}{\bf DT:} {\it #1}{\bf ]}}
\newcommand*{\fw}[1]{{ \bf [}{\bf FW:} {\it #1}{\bf ]}}
\newcommand*{\hy}[1]{{ \bf [}{\bf HY:} {\it #1}{\bf ]}}
\newcommand*{\jw}[1]{{ \bf [}{\bf JW:} {\it #1}{\bf ]}}

@@

\section{Introduction}
For data science practitioners, statistical inference is typically
just one step in a more elaborate analysis workflow. The first stage
of this work involves data acquisition, pre-processing and cleaning.
This is often followed by several iterations of exploratory model
design and testing of inference algorithms. Once a sufficiently
robust statistical model and a corresponding inference algorithm have
been identified, analysis results must be post-processed, visualized,
and in some cases integrated into a wider production system.

@@

\hy{Minor point. I got slightly confused by the last sentence. What does
``efficient in terms of the dimensionality ..'' mean?}
